### 2023-03-17 manuscript.tex
add coi [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/92e94ee4307718776393434199be15f82a344012.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/92e94ee4307718776393434199be15f82a344012/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/4449405877

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/d3c54909ec4078326089a0e58e4543abde78ce90/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/d3c54909ec4078326089a0e58e4543abde78ce90}{MMV-Lab/im2im-paper@d3c5490}
on March 17, 2023.

@@

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/92e94ee4307718776393434199be15f82a344012/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/92e94ee4307718776393434199be15f82a344012}{MMV-Lab/im2im-paper@92e94ee}
on March 17, 2023.

@@

\hypertarget{conflict-of-interest}{%
\subsection{Conflict of interest}\label{conflict-of-interest}}

The authors report no conflict of interest.
